 \documentclass[12pt, a4paper]{article} %, draft , twoside

\input{preamble.tex}
\addbibresource{references.bib}

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    citecolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
    breaklinks=true,
    pdfborder={0 0 0}
}
\setlist[itemize]{leftmargin=*, nosep, noitemsep}
\setlist[enumerate]{leftmargin=*, nosep, noitemsep, label=(\arabic*)}

\doublespacing{}

\begin{document}

\begin{titlepage}
	\colorbox{black!5}{%
		\parbox[t]{0.975\textwidth}{%
			\parbox[t]{0.95\textwidth}{%
				\raggedleft\vspace{0.75cm}\Huge\scshape
				Research Manual \\[7.5pt]
				\large\bfseries A Guide to Effective Policy Advocacy
				\vspace{0.75cm}
			}
		}
	}
	\vfill
	\parbox[t]{0.95\textwidth}{%
		\hfill\rule{0.15\linewidth}{0.5pt}\\[7.5pt]
		\raggedleft{}
		\textcopyright:{Zac Kienzle\textsuperscript{\textdagger}}\\[4pt]
		\normalsize\textsuperscript{\textdagger} University of Queensland, Brisbane, Australia\\
		\hfill\rule{0.15\linewidth}{0.5pt}
	}
\end{titlepage}

\tableofcontents

\section{Preliminary Setup}
This is a citation example
\citep{althaus_australian_2023}

\section{Resources and Toolings}
Where to go to get stuff moving.
Central repository of research already done.
Previous/sample papers annotated to get an idea of how to create

Templates
Links to take you to the Overleaf/whatever way we want to actually style documents.

\section{Research Workflows}
Websites to go to/ repos with evidence, papers, legal cases
Identify the best resources for each discipline, allowing us to learn from all our members. Send it around to see which links/websites we are missing.
Guide on how to effectively use Boolean searching and database searching. Links to databases and how to use them.
Pressing concerns/potential areas ripe for research/policy reform that may influence working groups (of course, this isn’t the only source of topic selection). Bills that are being passed, topical subjects.

\section{Advocacy Workflows}
How to translate long-form into short-form content as a learning experience to post on social media sites.

\section{Stylistic Conventions}
Fonts, general writing styles, excerpts from policy papers, publishing bodies and institutions we are trying to recreate the theming/styling from

\section{Integrity and Ethics Pledge}
Fair use of generative AI, machine translation, how to cite/attribute, how to use it effectively, plagiarism, integrity pledge and so on.


\printbibliography{}
\end{document}
